### 2024-06-19 analysis/analysis.qmd
update extractions
update analysis functions

@@

```{r}
metaMER_results <- do.call(rbind,
lapply(recoded_studies$model_rate_emotion_values, 
       parse_model_output)
)

>>>>

Initial work to build the data parser from the bibTeX files.

@@

```{r}
metaMER_results <-
do.call(
  rbind,
    lapply(1:nrow(recoded_studies),
       function(x) get_study_results(recoded_studies[x,])
       )
)
